---
title: "R Notebook"
output: html_notebook
---

# Momentum Trading

## Data loading

```{r loaddata, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(tidyverse)
library(datrader)
library(datools)
library(quantmod)
library(ggplot2)
library(xts)
library(TTR)

mypath<-'/home/michael/Dropbox/Development/trading'
mylist<- loadExistingInstruments(mypath)
```

We start by loading the data from our database. We can view the instruments present.

```{r}
names(mylist)
```

We will only focus on the most interesting ones for now which we'll define below.

```{r}
nasdaqSymbols<-c('MSFT', 'IBM', 'FB', 'GOOG', 'AMZN', 'NFLX',
                 'NVDA', 'AMD', 'INTC',
                 'TSLA', 'VLKAY', 'F')
```

We can have a look at how the Microsoft share has done over the years.

```{r msft, echo=FALSE, fig.width=10, message=FALSE, warning=FALSE, paged.print=FALSE}
chart_Series(mylist$MSFT)
```

## Trading strategy

We define a trading strategy as a function taking an xts time series featuring OHLC and based on a horizon decide weather to invest or not. The strategy we are concerned with in this notebook is the momentum strategy. It combines momentum together with risk. Basically it invests if

$$\frac{m(x)}{v(x)}>0$$
and holds the position until that condition is no longer true.

```{r}
momentumStrategy <- function(x, horizon=30){
  xhor <- tail(x, horizon)
  m <- tail(momentum(Cl(xhor), n=horizon-1), 1)[[1]]
  v <- tail(volatility(xhor, n=horizon), 1)[[1]]
  value <- m/v
  # browser()
  if(value > 0) return(list(Invest=TRUE))
  return(list(Invest=FALSE))
}
```

Before moving on we also need to define a function for generating positions based on a strategy. This can be achieved by this code.

```{r}
# Generate historical positions based on a trading strategy.
generateHistoricalPositions <- function(x, tstrat, h=60) {
  mypos<-rep(0,nrow(x))
  for(i in h:nrow(x)) mypos[i]<-ifelse(tstrat(x[(i-h):i,], h)$Invest==TRUE, 1, 0)
  mypos
}

# How many trades are made in this position vector?
numTrades<-function(p) length(which(abs(diff(p))>0))
```

Armed with this we can actually run through our symbols and apply our strategy. We do that by backtesting against a buy-and-hold strategy.

```{r}
mytib<-data.frame(Name=as.character(length(nasdaqSymbols)),
                  Trading=as.numeric(length(nasdaqSymbols)),
                  stringsAsFactors = FALSE)
for(i in 1:length(nasdaqSymbols)){
  cost <- 100/7 # 100 DKK in Dollars
  x<-mylist[[nasdaqSymbols[i]]]; h<-90;
  x<-tail(x, 1573)
  mypos<-generateHistoricalPositions(x, momentumStrategy, h)
  a<-dailyReturn(x)*mypos; a[which(a==0)]<-NA; a<-a[!is.na(a)]
  b<-dailyReturn(x)
  mytib[i, "Name"] <- nasdaqSymbols[i]
  mytib[i, "Trading"] <- length(which(a>0))/length(a)
  mytib[i, "Hold"] <- length(which(b>0))/length(b)
  mytib[i, "Trading1000"] <- prod(1+a)*1000 - numTrades(mypos)*cost
  mytib[i, "Hold1000"] <- prod(1+b)*1000 - cost
}
```

After running this we can see that our strategy actually beats buy and hold over a long period of time which is actually not bad at all.

```{r}
mytib %>% mutate(ImprovementIndex=100*round(Trading1000/Hold1000,2))
```

