---
title: "R Notebook"
output: html_notebook
---

## Trading on SP500

Now we're going to load the entire SP500 stocks into our list and backtest the momentum strategy on that. So let's first load the data.

```{r loadsp500data, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(tidyverse)
library(datrader)
library(datools)
library(quantmod)
library(ggplot2)
library(xts)
library(TTR)

source('functions.R')

mypath <- "~/Dropbox/Datasets/matrix/finance/data/sp500/csv"
mylist<- loadExistingInstruments(mypath)
mylist <- filterUnwantedStocks(mylist)
```

Here we have the same basic principle as before but now we'll also visualize a bit what's going on. We can show the price movements along with the indicators we are using for our decision making.

```{r AMAT, fig.width=10, message=FALSE, warning=FALSE, paged.print=FALSE}
chartSeries(mylist$AMAT)
chartSeries(mylist$MSFT, TA="addMomentum(n=90);addVolatility(n=90)")
```

In this example we'll show the development of Microsoft with momentum and volatility over a 90 day horizon.

```{r MSFT, fig.width=10, message=FALSE, warning=FALSE, paged.print=FALSE}
chartSeries(mylist$MSFT, TA="addMomentum(n=90);addVolatility(n=90)")
```

## Trading

We won't evaluate the entire SP500 right now but pick a few examples to evaluate at first. We will run a number of simulations and run them through one at a time. In all scenarios we invest 10000 USD.

### 10 random stocks from all years

```{r evaltenrandomallyears, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Random 10 stock full period
eval10allyearsdf <- evaluateStrategy(sample(mylist, 10), strategy = momentumStrategy, horizon = 90, cost = 1)
```

```{r}
eval10allyearsdf %>% knitr::kable()
```

Total profitability is `r sum(eval10allyearsdf$Trading1000) %>% scales::dollar()` compared to `r sum(eval10allyearsdf$Hold1000) %>% scales::dollar()`.

### 10 random stocks last year

```{r evaltenrandomlastyears, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Random 10 stocks last year
tmplist <- lapply(mylist, function(x) tail(x, 365))
eval10lastyeardf <- evaluateStrategy(sample(tmplist, 10), strategy = momentumStrategy, horizon = 90, cost = 1)
```

```{r}
eval10lastyeardf %>% knitr::kable()
```

Total profitability is `r sum(eval10lastyeardf$Trading1000) %>% scales::dollar()` compared to `r sum(eval10lastyeardf$Hold1000) %>% scales::dollar()`.

### 10 random stocks last 2 years

```{r evaltenrandomlast2years, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Random 10 stocks last 2 years
tmplist <- lapply(mylist, function(x) tail(x, 2*365))
eval10last2yeardf <- evaluateStrategy(sample(tmplist, 10), strategy = momentumStrategy, horizon = 90, cost = 1)
```

```{r}
eval10last2yeardf %>% knitr::kable()
```

Total profitability is `r sum(eval10last2yeardf$Trading1000) %>% scales::dollar()` compared to `r sum(eval10last2yeardf$Hold1000) %>% scales::dollar()`.
