---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# datrader

The goal of datrader is to help people do intelligent trading.

## Installing the package

You can install the latest bleeding version from this github repository.

```{r installing, eval=FALSE, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(devtools)
devtools::install_github('doktormike/datrader/datrader')
```

## Fetching data

```{r datafetching, echo=TRUE, fig.width=10, message=FALSE, warning=FALSE, paged.print=FALSE}
# Load library
library(datrader)
library(ggplot2)

# Download data into a new repository
mypath <- '/tmp'
mytickers <- c('FB', 'MSFT', 'NFLX')
downloadInstruments(instruments = mytickers, path = mypath, 
                    startDate = "2018-01-01")

# Load the data
mylist <- loadExistingInstruments(mypath)

# Plot the Facebook stock
chartSeries(mylist$FB)
```

## Building a portfolio

This is a basic example which shows you how to create a portfolio in a market. In this setting we fake the market by only loading three instruments from the package itself namely FB, MSFT and NFLX.

```{r portfoliocreation, echo=TRUE, fig.width=10, message=FALSE, warning=FALSE, paged.print=FALSE}
# Load library
library(datrader)
library(ggplot2)
library(scales)
library(gridExtra)

# Get data from package
mypath <- system.file('extdata', package = 'datrader')
mylist <- loadExistingInstruments(mypath)

# Define a function for ranking an instrument and selecting it for investment
rankInstrument <- function(x) tail(ROC(Cl(x), n=90), 1)[[1]]
myvol <- function(x) tail(volatility(x, n = 90, calc = 'garman.klass'), 1)[[1]]
selectInstrument <- function(x) rankInstrument(x)/myvol(x) > 0.05

# Create a portfolio from these functions
myport <- createPortfolio(mylist, selectInstrument, rankInstrument, topN=3)

# Display the prices and the portfolio weighting
p1 <- qplot(x=as.factor(1), y=myport, fill=factor(names(myport))) + 
  geom_bar(stat="identity", width = 1) + coord_polar(theta = "y") + 
  xlab("") + ylab("") + theme_minimal() + 
  scale_fill_brewer("Instrument", type = "qual", palette = 6)
p2 <- instrumentListToDataFrame(lapply(mylist, function(x) Cl(tail(x, 100)))) %>%
  ggplot(aes(y=value, x=as.Date(date), color=ticker, group=ticker)) + geom_line() + 
  facet_grid(ticker~., scales="free") + ylab("Price") + xlab("Date") + 
  theme_minimal() + 
  scale_x_date(labels = function(x) format(x, "%Y-%m")) +
  theme(axis.text.x = element_text(angle=60, vjust=0.5))
grid.arrange(p2, p1, ncol=2)
```

As you can see in the plot this small example focuses on investing in MSFT and NFLX since there has been very low momentum in FB. 

## Evaluating a strategy

We also would like to evaluate a strategy to see how much money it can make us over time. For this purpose the function evaluateStrategy exists. The first example shows a simple strategy which allows us to update our portfolio once every month.

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(datrader)
library(quantmod)
mypath <- system.file('extdata', package = 'datrader')
mylist <- loadExistingInstruments(mypath)
rankInstrument <- function(x) tail(momentum(Cl(x), n=90), 1)
selectInstrument <- function(x) rankInstrument(x) > 5
mystrat <- function(x) createPortfolio(x, selectInstrument, rankInstrument, 50)
mydates <- index(tail(mylist[[1]], 100))
result <- evaluateStrategy(mylist, mydates, mystrat, 30, 10000)
```

The result in this scenario for the last 100 days is `r result$Value` for an investment of 10000. Could be better. So let's try to do better.

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(datrader)
library(quantmod)
mypath <- system.file('extdata', package = 'datrader')
mylist <- loadExistingInstruments(mypath)
rankInstrument <- function(x) tail(momentum(Cl(x), n=90), 1)
selectInstrument <- function(x) rankInstrument(x) > 5
mystrat <- function(x) createPortfolio(x, selectInstrument, rankInstrument, 50)
mydates <- index(tail(mylist[[1]], 300))
result1 <- evaluateStrategy(mylist, mydates, mystrat, 30, 10000)
result1
```



